Draft

### 2021-01-15 SubGroup.Rmd
lancet

Referral <- subset(MDF, MDF$UseCase %in% "PrivatePublicReferral")
DOTS <- subset(MDF, MDF$UseCase %in% "PublicDOTSRetesting")
WalkIn <- subset(MDF, MDF$UseCase %in% "WalkIn")
# Missing <- subset(MDF, is.na(MDF$UseCase)==T)

@@

Referral_long  <- subset(MDF_long, MDF_long$UseCase %in% "PrivatePublicReferral")
DOTS_long  <- subset(MDF_long, MDF_long$UseCase %in% "PublicDOTSRetesting")
WalkIn_long  <- subset(MDF_long, MDF_long$UseCase %in% "WalkIn")

@@

```{r 2 AUC}
## All

library(precrec)
library(ggplot2)

@@

## Old only
l <- ROCPRC(Old)
Old <- data.frame(matrix(unlist(l), nrow=5, byrow=T))
Old$subgroup <- "Previously treated cases"

@@

## Referral only
l <- ROCPRC(Referral)
Referral <- data.frame(matrix(unlist(l), nrow=5, byrow=T))
Referral$subgroup <- "Referred"

@@

@@

aucTable <- rbind(all, New, Old, Young, Middle, Senior, Referral, DOTS, WalkIn, Female, Male)
colnames(aucTable) <- c("AI.Algorithm", "AUC", "PCAUC", "Subgroup")
write.csv(aucTable, "Results/aucTable.csv")
rm(list=(ls()))
```

@@

aucTable$Subgroup <- factor(aucTable$Subgroup, levels = c("Young age", "Middle age", "Old age", "Referred", "DOTS retested", "WalkIn", "New cases", "Previously treated cases", "Female", "Male"))
### AUC
age<-ggplot(aucTable[aucTable$Subgroup %in% c("Young age", "Middle age", "Old age"), ], aes(x=AI.Algorithm, y=AUC, fill=Subgroup)) +  geom_bar(stat="identity", width=0.6, position=position_dodge())+theme_minimal()+ theme(legend.position = "top")+  ylim(0, 0.95) + theme(panel.grid.minor = element_line(size=0.5)) + scale_y_continuous(minor_breaks = seq(0 , 0.95, 0.05), breaks = seq(0.65, 0.95, 0.05))

referral<-ggplot(aucTable[aucTable$Subgroup %in% c("Referred", "DOTS retested", "WalkIn"), ], aes(x=AI.Algorithm, y=AUC, fill=Subgroup)) + geom_bar(stat="identity", width=0.7, position=position_dodge())+theme_minimal()+ theme(legend.position = "top")+  ylim(0, 0.95) + theme(panel.grid.minor = element_line(size=0.5)) + scale_y_continuous(minor_breaks = seq(0 , 0.95, 0.05), breaks = seq(0.65, 0.95, 0.05))

@@

referralPC<-ggplot(aucTable[aucTable$Subgroup %in% c("Referred", "DOTS retested", "WalkIn"), ], aes(x=AI.Algorithm, y=PCAUC, fill=Subgroup)) + geom_bar(stat="identity", width=0.7, position=position_dodge())+theme_minimal()+ theme(legend.position = "top")+  ylim(0.3, 0.8) + theme(panel.grid.minor = element_line(size=0.5)) + scale_y_continuous(minor_breaks = seq(0 , 0.8, 0.05), breaks = seq(0.3, 0.8, 0.05))

@@

tiff("Results/PRC ROC AUC plot.tif", width = 18, height = 8, units = "in", res = 100)
require(gridExtra)

grid.arrange(age, referral, history, gender, agePC, referralPC, historyPC, genderPC, ncol=4)
# grid.arrange(age, referral, history, ncol=3)

dev.off()
# rm(age, referral, history, agePC, referralPC, historyPC, gender, genderPC)

>>>>

PrivateReferral <-subset(MDF, MDF$UseCase %in% "PrivateReferral")
PublicReferral <-subset(MDF, MDF$UseCase %in% "PublicReferral")
DOTS <-subset(MDF, MDF$UseCase %in% "PublicDOTSRetesting")
WalkIn <-subset(MDF, MDF$UseCase %in% "WalkIn")
Community <-subset(MDF, MDF$UseCase %in% "Community screening")
Contacts <-subset(MDF, MDF$UseCase %in% "Contacts")
# Missing <- subset(MDF, is.na(MDF$UseCase)==T)

@@

PrivateReferral_long <-subset(MDF_long, MDF_long$UseCase %in% "PrivateReferral")
PublicReferral_long <-subset(MDF_long, MDF_long$UseCase %in% "PublicReferral")
DOTS_long <-subset(MDF_long, MDF_long$UseCase %in% "PublicDOTSRetesting")
WalkIn_long <-subset(MDF_long, MDF_long$UseCase %in% "WalkIn")
Community_long <-subset(MDF_long, MDF_long$UseCase %in% "Community screening")
Contacts_long <-subset(MDF_long, MDF_long$UseCase %in% "Contacts")
# Missing <- subset(MDF_long, is.na(MDF_long$UseCase)==T)

@@

```{r 2 AUC}
## All
library(precrec)
library(ggplot2)

@@

## Old on ly
l <- ROCPRC(Old)
Old <- data.frame(matrix(unlist(l), nrow=5, byrow=T))
Old$subgroup <- "Previously treated cases"

@@

## PrivateReferral only
l <- ROCPRC(PrivateReferral)
PrivateReferral <- data.frame(matrix(unlist(l), nrow=5, byrow=T))
PrivateReferral$subgroup <- "PrivateReferral"

## PublicReferral only
l <- ROCPRC(PublicReferral)
PublicReferral <- data.frame(matrix(unlist(l), nrow=5, byrow=T))
PublicReferral$subgroup <- "PublicReferral"

@@

## Community only
l <- ROCPRC(Community)
Community <- data.frame(matrix(unlist(l), nrow=5, byrow=T))
Community$subgroup <- "Community"

## Contacts only
l <- ROCPRC(Contacts)
Contacts <- data.frame(matrix(unlist(l), nrow=5, byrow=T))
Contacts$subgroup <- "Contacts"

@@

aucTable <- rbind(all, New, Old, Young, Middle, Senior, PrivateReferral, PublicReferral, DOTS, WalkIn,Community, Contacts, Female, Male)

colnames(aucTable) <- c("AI.Algorithm", "AUC", "PCAUC", "Subgroup")
write.csv(aucTable, "Results/aucTable.csv")
rm(list=(ls()))
```

@@

aucTable$Subgroup <- factor(aucTable$Subgroup, levels = c("All","Young age", "Middle age", "Old age", "PrivateReferral", "PublicReferral", "DOTS", "WalkIn", "Community", "Contacts", "New cases", "Previously treated cases", "Female", "Male"))
### AUC
age<-ggplot(aucTable[aucTable$Subgroup %in% c("Young age", "Middle age", "Old age"), ], aes(x=AI.Algorithm, y=AUC, fill=Subgroup)) +  geom_bar(stat="identity", width=0.6, position=position_dodge())+theme_minimal()+ theme(legend.position = "top")+  ylim(0, 0.95) + theme(panel.grid.minor = element_line(size=0.5)) + scale_y_continuous(minor_breaks = seq(0 , 0.95, 0.05), breaks = seq(0.65, 0.95, 0.05))

referral<-ggplot(aucTable[aucTable$Subgroup %in% c("PrivateReferral", "PublicReferral", "DOTS", "WalkIn", "Community", "Contacts"), ], aes(x=AI.Algorithm, y=AUC, fill=Subgroup)) + geom_bar(stat="identity", width=0.7, position=position_dodge())+theme_minimal()+ theme(legend.position = "top")+  ylim(0, 0.95) + theme(panel.grid.minor = element_line(size=0.5)) + scale_y_continuous(minor_breaks = seq(0 , 0.95, 0.05), breaks = seq(0.65, 0.95, 0.05))

@@

referralPC<-ggplot(aucTable[aucTable$Subgroup %in% c("PrivateReferral", "PublicReferral", "DOTS", "WalkIn", "Community", "Contacts"), ], aes(x=AI.Algorithm, y=PCAUC, fill=Subgroup)) + geom_bar(stat="identity", width=0.7, position=position_dodge())+theme_minimal()+ theme(legend.position = "top")+  ylim(0.3, 0.8) + theme(panel.grid.minor = element_line(size=0.5)) + scale_y_continuous(minor_breaks = seq(0 , 0.8, 0.05), breaks = seq(0.3, 0.8, 0.05))

@@

tiff("Results/PRC ROC AUC plot 3.tif", width = 20, height = 8, units = "in", res = 110)
require(gridExtra)
grid.arrange(age, referral, history, gender, agePC, referralPC, historyPC, genderPC, ncol=4)
dev.off()

# rm(age, referral, history, agePC, referralPC, historyPC, gender, genderPC)
